Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-22 bdcloud_paper/latex/paper.tex
Edits to model description

\subsection{Generation of Customers}
For each proposed customer location zip code $z$, we compute the distance between $z$ and every store's zip code to find the closest store.  We compute the distance $d$ between $z$ and the zip code $s_z$ of the closest store.  The zip codes' latitudes and longitudes came from the Zip Code Database Project \cite{Zips}.  The weight $w_z$ for each zip code $z$ is modeled using an exponential distribution with the average distance $\beta$.

@@

To find the probabilities, the weights are normalized:

\begin{align*}
&p(\text{location} = \text{z}) = W^{-1} w_z \\
&W = \sum_{z} w(z) \nonumber
\end{align*}

@@

\subsubsection{Simulation of Transaction Times} \label{sec:transaction-times}
Transaction times are simulated using a Monte Carlo method (Figure~\ref{fig:trans_sim}).  The usage over time of each item category is simulated. The time between the customer's visit to the store to buy more items in each category and the exhaustion time of that item category is modeled using a Poisson process. Proposed transaction times for each item category are computed based on the exhaustion time and time sampled from the Poisson process. The earliest transaction time is taken as the overall proposed transaction time.  The probability of the transaction time is calculated using a PDF.  If rejected, new transaction times are proposed.  Otherwise, the purchased items are modeled using a separate process (discussed below). After the items are chosen, the process begins again with the simulation of the item category usages.

In the first stage of the process, the usage of items over time is modeled using a simple stochastic differential equation (SDE):

@@

The probability $p(X=i)$ of choosing item category $i$ is given by the normalizing the weight $w_i$ by the sum of all of the weights $W$:

\begin{align*}
&p(X=i) = W^{-1} w_i \\
&W = \sum_i w_i \nonumber
\end{align*}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/cluster_analysis.eps}
  \caption{Clustering of Brand and Flavor Purchasing Preferences}
  \label{fig:cluster_analysis}
\end{figure}

>>>>

\subsection{Generation of Customers}
For each proposed customer location zip code $z$, we compute the distance $d_m(z)$ between $z$ and each store's zip code $s_z$ to find the closest store.  The zip codes' latitudes and longitudes (taken from the Zip Code Database Project \cite{Zips}) are used to compute the distances. Each zip code $z$ is assigned a weight $w_z$ according to its distance $d_m(z)$ to the nearest store using an exponential distribution with the average distance $\beta$:

@@

The probability of choosing zip code $z$ is given by

\begin{equation*}
p(\text{location} = \text{z}) = \frac{w_z}{\sum_{z} w(z)}
\end{equation*}

@@

\subsubsection{Simulation of Transaction Times} \label{sec:transaction-times}
Transaction times are simulated using a Monte Carlo method (Figure~\ref{fig:trans_sim}).  The usage over time of each item category is simulated. Items categories are groups of items which are interchangeable such as ``dry dog food,'' ``dry cat food,'' and ``kitty litter.'' The time between the customer's visit to the store to buy more items in each category and the exhaustion time of that item category is modeled using a Poisson process. Proposed transaction times for each item category are computed based on the exhaustion time and time sampled from the Poisson process. The earliest transaction time is taken as the overall proposed transaction time.  The probability of the transaction time is calculated using a PDF.  If rejected, new transaction times are proposed.  Otherwise, the purchased items are modeled using a separate process (discussed below). After the items are chosen, the process begins again with the simulation of the item category usages.

In the first stage of the process, the usage of items over time is modeled using a stochastic differential equation (SDE):

@@

The probability $p(X=i)$ of choosing item category $i$ is given by

\begin{equation*}
p(X=i) = \frac{w_i}{\sum_i w_i}.
\end{equation*}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/cluster_analysis.eps}
  \caption{Clustering of Brand and Flavor Purchasing Preferences. Grey plus signs (+) represent customer data points, and cyan circles represent cluster centers.}
  \label{fig:cluster_analysis}
\end{figure}
